Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}

### 2019-04-15 manuscript.tex
almost done with revision

To begin, consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which shows estimated subgroup AMCEs for three features from the immigration study. In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in levels of support between the two subgroups. In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.

@@

For the \citeauthor{HainmuellerHopkinsYamamoto2014} language feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: F(4, 11496)=1.06, $p\leq0.37$. We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design.

Furthermore, we could also directly visualize differences in conditional marginal means for this feature --- and all features --- as in Figure \ref{fig:hainmueller_mm_diffs}. This provides a more direct presentation of \textit{differences} between subgroup preferences as the vertical line indicates feature levels for which there is no difference between the two groups. Positive values to the right of the line indicate positive differences (high ethnocentrism respondents are more favorable toward immigrants with this feature than low ethnocentrism respondents) and negative value to the left of zero convey the opposite. A further advantage of this plot is that unlike displays of conditional AMCEs, differences in conditional marginal means communicate subgroup differences for all feature levels including the reference categories. This display makes readily clear what was only indirectly apparent in Figure \ref{fig:hainmueller_mm_diffs}: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.

As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features. The result of that test for differences by ethnocentrism from the immigration experiment is: F(98, 11402)=1.16, $p\leq0.14$, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.

This kind of nested model comparison test can also be used to assess heterogeneity across conjoint features \citep[see also][]{EgamiImai2018}. For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9). Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to a quite different conclusion. As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences F(54, 67982)=3.72, $p\leq0.00$. This cross-country variation largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France. Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences, but ulimately there is no guarantee that they do in any particular analysis.

@@

@@

\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix-2}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix_split-1}

\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix_split-2}

@@

@@

>>>>

To begin, consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which shows estimated subgroup AMCEs for three features from the immigration study. In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in levels of support between the two subgroups thus distorting the size of differences at all other levels. In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.

@@

For the education feature, the resulting F-test for the model comparison in this case again gives us little reason to believe there are subgroup differences: F(7, 11493)=0.68, $p\leq0.69$. We could repeat such pairwise comparisons or omnibus comparisons for each feature in the design --- for country of origin (F(10, 11490)=1.56, $p\leq0.11$) or job (F(11, 11489)=0.87, $p\leq0.56$) --- or for all features as a whole (F(98, 11402)=1.16, $p\leq0.14$).

This visual display in Figure \ref{fig:hainmueller_mm_diffs} and these statistical tests make clear what could not be directly inferred from conditional AMCEs alone: there are indeed no sizeable and only a few statistically apparent differences in preferences between the two groups.

This kind of nested model comparison test can also be used to assess heterogeneity across conjoint features \citep[see also][]{EgamiImai2018}. For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9). Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to quite different inferences. As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries [Germany, France, United States, United Kingdom] largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences F(54, 67982)=3.72, $p\leq0.00$. This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France. Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences (as in the \citeauthor{HainmuellerHopkinsYamamoto2014} case), but ulimately there is no guarantee that they do in any particular analysis.

@@

\subsection{Replication using AMCEs}

@@

@@

\subsection{Replication using MMs}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_mm_appendix-1}

@@

%\clearpage

%\subsection{Numerical Results: AMCEs}

%\clearpage

%\subsection{Numerical Results: MMs}
